\newpage
\thispagestyle{empty}
\mbox{}
%\newpage\null\thispagestyle{empty}\newpage
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
Firstly, I would like to thank my supervisors, Dr Ivo Tews and Dr Gwyndaf Evans, for giving me the opportunity to work on this project. Without your guidance, advice and enthusiasm, the completion of this project would not have been possible.

All of the experiments described in this thesis were dependent on the funding and facilities provided by the University of Southampton and Diamond Light Source. I am grateful to Dr Robin Owen and Dr Pierre Aller at Diamond for their help with scripting the processing of X-ray diffraction data. I would also like to thank Prof. Arwen Pearson, for providing assistance with scripting and insightful discussions about enzymology, crystallography and radiation damage.       

I would like to thank the European Synchrotron Radiation Facility for the generous allocation of beamtime to the experiments that were performed in this project. I would like to extend my thanks to Dr Antoine Royant, Dr Guillaume Gotthard and Dr David von Stetten for their assistance with the spectroscopy experiments conducted at the ESRF.

I would like to thank Dr Stuart Findlow and Christopher Holes for running the crystallisation facility in Southampton. I would also like to thank Dr Volker Windeisen, Dr John Butler and Dr Halina Mikolajek for sharing their expertise in the lab regarding the molecular biology and protein purification side of the project.

Thanks to all of the members of the structural biology department in Southampton for making the lab an enjoyable place to work. In particular, I would like to thank Curtis Phippen, Andy Hutchin, Billy Anderson, Ben Yarnall, Moritz Machelett, Chris Orr, Jordana Griffiths and Kelly Buggy.  

Finally, I would like to thank my family, especially my parents, for their constant support and encouragement.
\cleardoublepage